Title of the publication

### 2016-06-14 documentation/EnTrI2/manuscript.tex
Wrote a part of introduction, tested redefining insertion indices using number of reads, tested using a mixture of gamma distributions
Tested mixtools with Lars' initial values, Regenerated the species tree with raxml and bootstrap values, Ran Hieranoid, Defined core and accessory on hieranoid results

\usepackage{amssymb,amsfonts,amsmath}

@@

Enterobacteriaceae is a family that includes bacteria with different host ranges and pathogenecity found in soil, water, plants, animals and humans \cite{brenner_bergeys_2006}. In humans, various strains from this family can cause diarrhoea, septicaemia, urinary tract infection, meningitis, respiratory disease, and wound and burn infection \cite{brenner_bergeys_2006}. Besides, they can infect poultry and livestocks and cause financial losses for farmers \cite{brenner_bergeys_2006}. Here, we perform a transposon-directed insertion-site sequencing experiment to study the conservation of essentiality in strains from 5 different species in this family.

@@

\section{Results}

We have studied the essentiality of genes in 12 strains from Enterobacteriaceae family. The species are depicted in Fig~\ref{fig:tree}.

@@

%----------------------------------------------------------------------------------------
%	FIGURES AND TABLES
%----------------------------------------------------------------------------------------
\begin{figure}
\includegraphics[scale=0.25]{consensus-tree.pdf}
\label{fig:tree}
\caption{Species tree. How is it made?}
\end{figure}

>>>>

\usepackage{amssymb,amsfonts,amsmath}
\usepackage{color}

@@

Enterobacteriaceae is a family that includes bacteria with different host ranges and pathogenecity found in soil, water, plants, animals and humans \cite{brenner_bergeys_2006}. In humans, various strains from this family can cause diarrhoea, septicaemia, urinary tract infection, meningitis, respiratory disease, and wound and burn infection \cite{brenner_bergeys_2006}. Besides, they can infect poultry and livestocks and cause financial losses for farmers \cite{brenner_bergeys_2006}. Here, we perform a transposon-directed insertion-site sequencing experiment to study the conservation of essentiality of genes in strains from 5 different species in this family.

\textcolor{red}{\{A summary of what we have done\}}

@@

\section{Results}
\textcolor{red}{\{An explanation of the experiment\}}

\textbf{Clustering orthologous and paralogous genes.} To study the essentiality of genes in 12 strains depicted in Fig~\ref{fig:tree}, We needed to cluster sets of orthologous genes in these strain. Plenty of methods are proposed for this purpose. Altenhoff et al.\@ have compared 15 of these methods \cite{altenhoff_standardized_2016} and shown that Hieranoid \cite{schreiber_hieranoid:_2013} is among three methods that keep a balance between precision and recall. We have used Hieranoid to cluster the sets of orthologous genes. In addition, we intended to study the essentiality of genes in paralogous genes. For this, we have developed a program that clusters all homologous genes using Jackhmmer from HMMER3 package \cite{mistry_challenges_2013}.

@@

%----------------------------------------------------------------------------------------
%	FIGURES AND TABLES
%----------------------------------------------------------------------------------------
\begin{figure}
\includegraphics[scale=0.25]{consensustree.pdf}
\label{fig:tree}
\caption{Species tree. How is it made?}
\end{figure}
